Model Based Analysis of Patient Derived Xenograft Growth Curves

### 2022-04-27 paper_Kuhlers.Rmd
more edits

PDX models have significant advantages over alternative models.
Standard *in vitro* models typically undergo transformations
to ensure proper growth and are kept in growth media that is drastically
different from the tumor enviroment *in vivo*. Additionally, these models
are "two dimensional" and all three dimensional interactions are
lost with cell lines (**REFS**).
PDX models preserve the 3D nature of human tumors and do not require
transformation, thereby also preserving the genomic characteristics of the
donor tissue (**REFS**).

>>>>

PDX models have significant advantages over alternative models.
Standard *in vitro* models typically undergo transformations
to ensure proper growth and are kept in growth media that is drastically
different from the tumor enviroment *in vivo*. Additionally, these models
are "two dimensional" and all three dimensional interactions are
lost with cell lines (Tentler, Pompili)
PDX models preserve the spatial nature of human tumors and do not require
transformation, thereby also preserving the genomic characteristics of the
donor tissue (Tentler)

The PDX Development and Trial Centers Research Network (PDXNet) is an
NCI sponsored consortium aimed at using PDX models to investigate
cancer therapies and reduce the time therapies move from pre-clinical
to clinical stages (PDXnet Website). Much of the work from the PDXNet
has focused on genomic characterization,
